Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-05 ms.tex
still reworking bandpass correction discussion

@@

% at the end of this section state that we do all of our fits etc. with
% both models (call one of them model 1, and the other model 2, similar
% to what FDS99 did

@@

\subsection{Finite Bandpass Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. In practice, 
however, we wish to constrain our model using measurements in the broad 
\IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have therefore 
computed dimensionless bandpass correction factors:$b_{\nu_i}(T, \alpha)$

\begin{equation}
b_{\nu_i}(T, \alpha) = 
\end{equation}

The two-component model prediction in band $\nu_i$ is then constructed
as a linear combination of color-corrected MBB terms as:

\begin{equation}
M_{\nu_i}b_{\nu_i}
\end{equation}

@@

Is the predicted observation for the \PLANCK~or \IRAS~band of interest, in 
MJy/sr. Here $\nu_i$ represents the $i^{th}$ of the 
five nominal band center frequencies for which we have broadband measurements, 
$\nu_i \in$ \{217, 353, 545, 857, 3000\} GHz. We have used the 
\PLANCK~transmission curves provided in the file \verb|HFI_RIMO_R1.10.fits| 
\citep{planckresponse}. For 3000 GHz, we have used the DIRBE bandpass.

@@

The \PLANCK~217 GHz and 353 GHz data are provided in units of thermodynamic 
$\delta T$, while \verb|i100| and the higher frequency \PLANCK~maps are 
provided in units of MJy/sr. Although the aforementioned preprocessing steps 
were conducted with each map in its native units, we converted the 217 GHz and 
353 GHz measurements to MJy/sr according to \cite{planckresponse} prior to 
performing SED fits.

>>>>

% does this statement accidentally give the impression that I do separate 
% MCMC fits, one in which i fit Planck/IRAS **data** and one in which
% i fit FIRAS/IRAS data ????

@@

@@

\subsection{Finite Bandpass Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density $M_{\nu}$ in e.g. MJy/sr for any single frequency $\nu$. In 
practice, however, we wish to constrain our model using measurements in the 
broad \IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have 
therefore computed dimensionless bandpass correction factors:

\begin{equation}
b_{\nu_i}(T, \beta) = \frac{\int \mathcal{T}(\nu)\nu^{\beta}B_{\nu}(T) d\nu \bigg[\int \mathcal{T}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
\end{equation}

% now i need to define what \nu_{i,c} is (it's the nominal central 
% frequency of band \nu_i) e.g. 857 GHz for Planck 857, etc..

% also need to define what \mathcal{T} is (planck transmission, 
% dimensionless)

The two-component model prediction in band $\nu_i$ is then constructed
as a linear combination of color-corrected MBB terms:

\begin{equation}
\tilde{I}_{\nu_i} \propto \sum_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k)
\end{equation}

Note that by convention $f_2$=(1$-$$f_1$)

@@

Is the predicted observation for the \PLANCK~or \IRAS~band of interest. Here 
$\nu_i$ represents the $i^{th}$ of the five nominal band center frequencies for
which we have broadband measurements, $\nu_i \in$ \{217, 353, 545, 857, 3000\} 
GHz. We have used the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have used 
the DIRBE bandpass.

@@

The \PLANCK~100-353 GHz data are provided in units of thermodynamic 
$\delta T$, while \verb|i100| and the higher frequency HFI maps are provided in
units of MJy/sr. Although the aforementioned preprocessing steps were conducted
with each map in its native units, we converted the 217 GHz and 353 GHz 
measurements to MJy/sr according to \cite{planckresponse} prior to performing 
SED fits.
